Adaptive broadcast tree for multicores

### 2013-06-07 graphs/visu_gruyere_ring.tex
New visualization applied to all combinations of machines and topologies except for rings

\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
\node at (0mm,0mm) {core 00};
\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: mst};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
\draw[->] (s_0_3.center) -- (r_0_3.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
\draw[->] (s_0_2.center) -- (r_0_2.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
\draw[->] (s_0_1.center) -- (r_0_1.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
\draw[->] (s_16_19.center) -- (r_16_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
\draw[->] (s_4_7.center) -- (r_4_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
\draw[->] (s_16_18.center) -- (r_16_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
\draw[->] (s_16_17.center) -- (r_16_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
\draw[->] (s_4_6.center) -- (r_4_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
\draw[->] (s_20_23.center) -- (r_20_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
\draw[->] (s_4_5.center) -- (r_4_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
\draw[->] (s_20_22.center) -- (r_20_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
\draw[->] (s_8_11.center) -- (r_8_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
\draw[->] (s_28_31.center) -- (r_28_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
\draw[->] (s_20_21.center) -- (r_20_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
\draw[->] (s_28_30.center) -- (r_28_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
\draw[->] (s_24_27.center) -- (r_24_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
\draw[->] (s_8_10.center) -- (r_8_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
\draw[->] (s_12_15.center) -- (r_12_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
\draw[->] (s_24_26.center) -- (r_24_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
\draw[->] (s_28_29.center) -- (r_28_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
\draw[->] (s_8_9.center) -- (r_8_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
\draw[->] (s_12_14.center) -- (r_12_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
\draw[->] (s_24_25.center) -- (r_24_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
\draw[->] (s_12_13.center) -- (r_12_13.center);

>>>>

\node (core_0_label) at (0mm,0mm) {core 00};
\node (core_1_label) at (0mm,5mm) {core 01};
\node (core_2_label) at (0mm,10mm) {core 02};
\node (core_3_label) at (0mm,15mm) {core 03};
\node (core_4_label) at (0mm,20mm) {core 04};
\node (core_5_label) at (0mm,25mm) {core 05};
\node (core_6_label) at (0mm,30mm) {core 06};
\node (core_7_label) at (0mm,35mm) {core 07};
\node (core_8_label) at (0mm,40mm) {core 08};
\node (core_9_label) at (0mm,45mm) {core 09};
\node (core_10_label) at (0mm,50mm) {core 10};
\node (core_11_label) at (0mm,55mm) {core 11};
\node (core_12_label) at (0mm,60mm) {core 12};
\node (core_13_label) at (0mm,65mm) {core 13};
\node (core_14_label) at (0mm,70mm) {core 14};
\node (core_15_label) at (0mm,75mm) {core 15};
\node (core_16_label) at (0mm,80mm) {core 16};
\node (core_17_label) at (0mm,85mm) {core 17};
\node (core_18_label) at (0mm,90mm) {core 18};
\node (core_19_label) at (0mm,95mm) {core 19};
\node (core_20_label) at (0mm,100mm) {core 20};
\node (core_21_label) at (0mm,105mm) {core 21};
\node (core_22_label) at (0mm,110mm) {core 22};
\node (core_23_label) at (0mm,115mm) {core 23};
\node (core_24_label) at (0mm,120mm) {core 24};
\node (core_25_label) at (0mm,125mm) {core 25};
\node (core_26_label) at (0mm,130mm) {core 26};
\node (core_27_label) at (0mm,135mm) {core 27};
\node (core_28_label) at (0mm,140mm) {core 28};
\node (core_29_label) at (0mm,145mm) {core 29};
\node (core_30_label) at (0mm,150mm) {core 30};
\node (core_31_label) at (0mm,155mm) {core 31};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_4) at (30mm,40mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_12) at (36mm,40mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_11) at (42mm,40mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_10) at (48mm,40mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_9) at (54mm,40mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_4) at (42mm,20mm) {};
\draw[->,semithick,color=red] ($(s_8_4.east)-(1mm,0mm)$) -- ($(r_8_4.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_0) at (48mm,20mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_7) at (54mm,20mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_6) at (60mm,20mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_5) at (66mm,20mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_12) at (48mm,60mm) {};
\draw[->,semithick,color=red] ($(s_8_12.east)-(1mm,0mm)$) -- ($(r_8_12.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_28) at (54mm,60mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_15) at (60mm,60mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_14) at (66mm,60mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_13) at (72mm,60mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_11) at (48mm,55mm) {};
\draw[->] ($(s_8_11.east)-(1mm,0mm)$) -- ($(r_8_11.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_10) at (54mm,50mm) {};
\draw[->] ($(s_8_10.east)-(1mm,0mm)$) -- ($(r_8_10.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_0) at (60mm,0mm) {};
\draw[->,semithick,color=red] ($(s_4_0.east)-(1mm,0mm)$) -- ($(r_4_0.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_16) at (66mm,0mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_3) at (72mm,0mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_2) at (78mm,0mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_1) at (84mm,0mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_7) at (60mm,35mm) {};
\draw[->] ($(s_4_7.east)-(1mm,0mm)$) -- ($(r_4_7.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_9) at (60mm,45mm) {};
\draw[->] ($(s_8_9.east)-(1mm,0mm)$) -- ($(r_8_9.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_28) at (66mm,140mm) {};
\draw[->,semithick,color=red] ($(s_12_28.east)-(1mm,0mm)$) -- ($(r_12_28.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_24) at (72mm,140mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_31) at (78mm,140mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_30) at (84mm,140mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_29) at (90mm,140mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_6) at (66mm,30mm) {};
\draw[->] ($(s_4_6.east)-(1mm,0mm)$) -- ($(r_4_6.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_15) at (66mm,75mm) {};
\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_5) at (72mm,25mm) {};
\draw[->] ($(s_4_5.east)-(1mm,0mm)$) -- ($(r_4_5.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_14) at (72mm,70mm) {};
\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_16) at (78mm,80mm) {};
\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_20) at (84mm,80mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_19) at (90mm,80mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_18) at (96mm,80mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_17) at (102mm,80mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_13) at (78mm,65mm) {};
\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_3) at (78mm,15mm) {};
\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_24) at (84mm,120mm) {};
\draw[->,semithick,color=red] ($(s_28_24.east)-(1mm,0mm)$) -- ($(r_28_24.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_8) at (90mm,120mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_27) at (96mm,120mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_26) at (102mm,120mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_25) at (108mm,120mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_31) at (84mm,155mm) {};
\draw[->] ($(s_28_31.east)-(1mm,0mm)$) -- ($(r_28_31.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_2) at (84mm,10mm) {};
\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_30) at (90mm,150mm) {};
\draw[->] ($(s_28_30.east)-(1mm,0mm)$) -- ($(r_28_30.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_1) at (90mm,5mm) {};
\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_20) at (96mm,100mm) {};
\draw[->,semithick,color=red] ($(s_16_20.east)-(1mm,0mm)$) -- ($(r_16_20.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_8) at (102mm,100mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_23) at (108mm,100mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_22) at (114mm,100mm) {};
\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_21) at (120mm,100mm) {};
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_19) at (96mm,95mm) {};
\draw[->] ($(s_16_19.east)-(1mm,0mm)$) -- ($(r_16_19.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_29) at (96mm,145mm) {};
\draw[->] ($(s_28_29.east)-(1mm,0mm)$) -- ($(r_28_29.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_8) at (102mm,40mm) {};
\draw[->,semithick,color=red] ($(s_24_8.east)-(1mm,0mm)$) -- ($(r_24_8.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_18) at (102mm,90mm) {};
\draw[->] ($(s_16_18.east)-(1mm,0mm)$) -- ($(r_16_18.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_27) at (102mm,135mm) {};
\draw[->] ($(s_24_27.east)-(1mm,0mm)$) -- ($(r_24_27.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_26) at (108mm,130mm) {};
\draw[->] ($(s_24_26.east)-(1mm,0mm)$) -- ($(r_24_26.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_17) at (108mm,85mm) {};
\draw[->] ($(s_16_17.east)-(1mm,0mm)$) -- ($(r_16_17.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_23) at (114mm,115mm) {};
\draw[->] ($(s_20_23.east)-(1mm,0mm)$) -- ($(r_20_23.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_25) at (114mm,125mm) {};
\draw[->] ($(s_24_25.east)-(1mm,0mm)$) -- ($(r_24_25.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_8) at (120mm,40mm) {};
\draw[->,semithick,color=red] ($(s_20_8.east)-(1mm,0mm)$) -- ($(r_20_8.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_22) at (120mm,110mm) {};
\draw[->] ($(s_20_22.east)-(1mm,0mm)$) -- ($(r_20_22.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_21) at (126mm,105mm) {};
\draw[->] ($(s_20_21.east)-(1mm,0mm)$) -- ($(r_20_21.west)+(1mm,0mm)$); 
\begin{pgfonlayer}{background}
\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_8_10) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_8_9) (r_4_7) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_4_6) (r_12_15) (r_4_5) (r_12_14) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_12_13) (r_0_3) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_0_2) (r_28_31) (r_0_1) (r_28_30) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_28_29) (r_16_19) (r_24_8) (r_16_18) (r_24_27) (r_24_26) (r_16_17) (r_20_23) (r_24_25) (r_20_8) (r_20_22) (r_20_21) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_8_10) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_4_7) (r_8_9) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_4_6) (r_12_15) (r_4_5) (r_12_14) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_12_13) (r_0_3) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_28_31) (r_0_2) (r_28_30) (r_0_1) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_16_19) (r_28_29) (r_24_8) (r_16_18) (r_24_27) (r_24_26) (r_16_17) (r_20_23) (r_24_25) (r_20_8) (r_20_22) (r_20_21)] (allobjects) {};
